### 2022-02-10 cleave.tex
complex loops

Implementation-wise, \ac{CLEAVE} is built on top of the well-established and stable \emph{Twisted}\footnote{\url{https://twistedmatrix.com}} asynchronous programming and networking framework.
The aforementioned core components (\emph{State}, \emph{Controller}, \emph{Sensors}, and \emph{Actuators}) are provided as abstract base classes with core functionality that users must extend for their specific use cases and \acp{NCS}.
On the other hand, the framework handles network communication and metric collection autonomously; users only need to select the desired transport protocol (we do however provide an \ac{API} for extending the available transports).

@@

>>>>

Implementation-wise, \ac{CLEAVE} is built on top of the well-established and stable \emph{Twisted}\footnote{\url{https://twistedmatrix.com}} asynchronous programming and networking framework.
The aforementioned core components (\emph{State}, \emph{Controller}, \emph{Sensors}, and \emph{Actuators}) are provided as abstract base classes with core functionality that users must extend for their specific use cases and \acp{NCS}.
The framework makes no assumptions about the inner workings of the user implementations of these classes other than the interfaces they expose.
Users are therefore free to implement arbitrarily complex functionality in these components.
On the other hand, \ac{CLEAVE} handles network communication and metric collection autonomously; users only need to select the desired transport protocol (we do however provide an \ac{API} for extending the available transports).

@@

Although the core design of \ac{CLEAVE} follows a single-loop approach, multi-loop scenarios can be easily implemented through the combination of multiple \ac{CLEAVE} instances.
Furthermore, the framework makes no assumptions about the individual components other than the signatures of methods on the base classes that must be extended and implemented.
Combined with the plain-Python emulation configuration scripts, this makes development of more complex scenarios merely a matter of implementing the desired functionality within the framework itself.
